\Large \bf Lissy: Experimenting with on-chain order books

### 2021-09-13 LaTeX-LNCS-2022/sections/abstract.tex
Finalized :boom:

Financial regulators have long-standing concerns about fully decentralized exchanges that run `on-chain' without any obvious regulatory hooks. The popularity of Uniswap, an automated market makers (AMM), made these concerns a reality. AMMs implement a lightweight dealer-based trading system, but they are unlike anything on Wall Street, require fees intrinsically, and are susceptible to front-running attacks. This leaves the following research questions we address in this paper: (i) are conventional (\ie orderbooks), secure (\ie resistant to front-running and price manipulation) and fully decentralized exchanges feasible on a public blockchain like Ethereum, (ii) what is the performance profile, and (iii) how much do Layer 2 techniques (\eg Arbitrum) increase performance? To answer these questions, we implement, benchmark, and experiment with an Ethereum-based call market exchange called \cm. We confirm the functionality is too heavy for Ethereum today (you cannot expect to exceed a few hundred trade executions per block) but show it scales dramatically (99.88\% gas cost reduction) on Arbitrum.

>>>>

Financial regulators have long-standing concerns about fully decentralized exchanges that run `on-chain' without any obvious regulatory hooks. The popularity of Uniswap, an automated market makers (AMM), made these concerns a reality. AMMs implement a lightweight dealer-based trading system, but they are unlike anything on Wall Street, require fees intrinsically, and are susceptible to front-running attacks. This leaves the following research questions we address in this paper: (1) are conventional (\ie order books), secure (\ie resistant to front-running and price manipulation) and fully decentralized exchanges feasible on a public blockchain like Ethereum, (2) what is the performance profile, and (3) how much do Layer 2 techniques (\eg Arbitrum) increase performance? To answer these questions, we implement, benchmark, and experiment with an Ethereum-based call market exchange called \cm. We confirm the functionality is too heavy for Ethereum today (you cannot expect to exceed a few hundred trade executions per block) but show it scales dramatically (99.88\% gas cost reduction) on Arbitrum.

### 2021-09-13 LaTeX-LNCS-2022/sections/appendix.tex
edits on L2 diagram and table
Finalized :boom:

At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}. So in order to account for refunds in  Tables~\ref{tab:PQUnitTests}, we calculate them manually. First, we determine exactly how many storage slots are being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 or 15,000 respectively.

@@

\begin{sidewaysfigure}
\centering
\includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
\caption{\footnotesize{Overview of \cm on Arbitrum.}  \label{fig:lissyl2}}
\end{sidewaysfigure}

@@

\paragraph{Centralized Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.

@@

\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications. This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one. Automated market makers  (\eg Uniswap v3) have all the trust advantages of an on-chain order book, plus they are relatively more efficient. The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory. This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees. By contrast, an order book requires no upfront inventory and trading fees are optional. Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define. We leave it as an assertion that with equal liquidity, order books have more favorable price dynamics for traders.

@@

\subsection{Call Markets}
Assume traders submit their orders in Table~\ref{tab:cmsample} to a call market once it is open. In the following, we explain how these orders are executed.
\input{tables/cm.tex}

\label{app:cm}
\begin{itemize}
\item The call market first matches Alice ask order to sell 1 at 10 with Avni's bid order to Buy 3 at 12. The trader happens at the price Alice asks for; 10, and 2 will be given to the miner as a price improvement. This trade fills Alice's order and leaves Avni with a remainder of 2 to buy at 12. 
\item Next, the call market matches Avni's remainder of 2 with the next highest priority ask order in the list which is Navjot's order to sell 4 at 10.15. Trade occurs at 10.15 and 1.85 will be given to the miner as a price improvement. This trade fills the remainder of Avni's bid order and leaves Navjot with a remainder of 2 to sell at 10.15.
\item The market now matches the next highest bid order in the list, Bob's bid order to buy 1 at 12.15, with the remainder of Navjot ask order to sell 2 at 10.15. Trader occurs at 10.15 and 2 will be given to minder as a price improvement. This trader fills Bob bid order and leaves Navjot with a remainder of 1 to sell at 10.15.
\item Next, the market matches Kritee's bid order to buy 3 at 13 with the remainder of Navjot's ask order to sell 1 at 10.15. Trade occurs at 10.15 and 2.85 will be given to miner as a price improvement. This match fills the Navjot's order and leaves Kritee with a remainder of 2 to buy at 13.
\item The market then matches Mehdi's ask order to sell 4 at 10.18 with the remainder of Kritee's bid order to buy 2 at 13. Trade occurs at 10.18 and 2.82 is given to miner as a price improvement. This trade fills Kritee's order and leaves Mehdi with a remainder of 2 to sell at 10.18 unfilled. 
\end{itemize}

@@

in \cm, both the tokens and ETH that a trader wants to potentially use in the order book are pre-loaded into the contract. Consider Alice, who holds a token and decides she wants to trade it for ETH. In this model, she must first transfer the tokens to the contract and then submit an ask order. If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert. If she waits for confirmation, this introduces a delay. This delay seems reasonable but we point out a few options it could be addressed:

@@

Call markets are heralded for fair price discovery. This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivatives settle based on the closing price). We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so. This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them. Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling median of prices over time, and (2) using it alongside other sources for the same price and forming a consensus. While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.

>>>>

At the time of this writing, Ethereum transaction receipts only account for the \texttt{gasUsed}, which is the total amount of gas units spent during a transaction, and users are not able to obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}. So in order to account for refunds in Table~\ref{tab:PQUnitTests}, we calculate them manually. First, we determine exactly how many storage slots are being cleared or how many smart contracts are being destroyed, then we multiply these numbers by 24,000 or 15,000 respectively.

@@

\begin{figure}[htb]
  \centering
  \begin{turn}{90}
  \begin{minipage}{8in}
  \centering
\includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
  \caption{\footnotesize{Overview of \cm on Arbitrum.}
\label{fig:lissyl2}}
  \end{minipage}
  \end{turn}
\end{figure}

@@

\paragraph{Centralized Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been leveled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.

@@

\paragraph{On-chain Dealers.} An advantage of on-chain trading is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications. This has fueled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one. Automated market makers  (\eg Uniswap v3) have all the trust advantages of an on-chain order book, plus they are relatively more efficient. The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory. This inventory is loaded into the DApp by an investor who will not profit from the trades themselves but hopes their losses (termed `impermanent losses') are offset over the long-term by trading fees. By contrast, an order book requires no upfront inventory and trading fees are optional. Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define. We leave it as an assertion that with equal liquidity, order books have more favorable price dynamics for traders.

@@

\subsection{Call Markets}
Assume traders submit their orders in Table~\ref{tab:cmsample} to a call market when it is open. In the following, we explain how these orders are executed:
\input{tables/cm.tex}

\label{app:cm}
\begin{itemize}
\item The call market first matches Alice's ask order to sell 1 at 10 with Avni's bid order to buy 3 at 12. Trade occurs at the price Alice asks for; 10, and 2 will be given to the miner as a price improvement. This trade fills Alice's order and leaves Avni with a remainder of 2 to buy at 12. 
\item Next, the call market matches Avni's remainder of 2 with the next highest priority ask order in the list which is Navjot's order to sell 4 at 10.15. Trade occurs at 10.15 and 1.85 will be given to the miner as a price improvement. This trade fills the remainder of Avni's bid order and leaves Navjot with a remainder of 2 to sell at 10.15.
\item The market now matches the next highest bid order in the list, Bob's bid order to buy 1 at 12.15, with the remainder of Navjot's ask order to sell 2 at 10.15. Trader occurs at 10.15 and 2 will be given to miner as a price improvement. This trade fills Bob's bid order and leaves Navjot with a remainder of 1 to sell at 10.15.
\item Next, the market matches Kritee's bid order to buy 3 at 13 with the remainder of Navjot's ask order to sell 1 at 10.15. Trade occurs at 10.15 and 2.85 will be given to miner as a price improvement. This trade fills Navjot's order and leaves Kritee with a remainder of 2 to buy at 13.
\item The market then matches Mehdi's ask order to sell 4 at 10.18 with the remainder of Kritee's bid order to buy 2 at 13. Trade occurs at 10.18 and 2.82 is given to miner as a price improvement. This trade fills Kritee's order and leaves Mehdi with a remainder of 2 to sell at 10.18 unfilled. 
\end{itemize}

@@

in \cm, both the tokens and ETH that a trader wants to potentially use in the order book are preloaded into the contract. Consider Alice, who holds a token and decides she wants to trade it for ETH. In this model, she must first transfer the tokens to the contract and then submit an ask order. If she does this within the same block, there is a chance that a miner will execute the ask before the transfer and the ask will revert. If she waits for confirmation, this introduces a delay. This delay seems reasonable but we point out a few options it could be addressed:

@@

Call markets are heralded for fair price discovery. This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well published) and operationally (many derivatives settle based on the closing price). We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so. This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them. Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling median of prices over time, and (2) using it alongside other sources for the same price and forming a consensus. While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.
